Multisensor Architecture for an Intersection Management System

### 2019-01-22 ch3-arch_sys.tex
Removed TODOs and added revision history. Updated version

\todo{Check stages description and figure}

@@

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), and once loaded in Redis, it is available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in different languages. In addition,  it is possible to create simple scripts to interact with the system. Below are described the two types of data used by the systems: the .imscfg file and the messages and configuration parameters.

>>>>

%\todo{Check stages description and figure}

@@

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), and once loaded in Redis, it is available for any client requiring it.

%\todo{Define JSON HERE!!!!}

@@

%\todo{Move JSON definition from here!!!}

Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in different languages. In addition,  it is possible to create simple scripts to interact with the system. Below are described the two types of data used by the systems: the .imscfg file and the messages and configuration parameters.

### 2019-01-22 last_version.tex
Corrections and figures updated.
Corrections in ch 1, 2 and 5
Added TODOs
Removed TODOs and added revision history. Updated version

\begin{titlepage}
    \begin{center}
%        \vspace*{1cm}
%        \Huge        
%        Multisensor Architecture for an Intersection Management System
%   
%        \vspace{3.5cm}
%        \LARGE
%        Gustavo Adolfo Velasco-Hernandez
%        
%        \vfill
%        \large
%		        
%        
%        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
%        
%        \vspace{2cm}
%        
%        Advisor: Prof. Eduardo Caicedo Bravo
%		
%		\vspace{2cm}
%        
%        %\includegraphics[width=0.4\textwidth]{university}
%        Perception and Intelligent Systems Research Group \\
%        School of Electrical and Electronics Engineering\\
%        Universidad del Valle\\
%        Colombia\\
%        \today
%\vfill

Version: 0.8 \\
\vspace{2cm}
An updated version of this report can be downloaded from: \\
\href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}      
    \end{center}
\end{titlepage}

>>>>

\begin{titlepage}
    \begin{center}
%        \vspace*{1cm}
%        \Huge        
%        Multisensor Architecture for an Intersection Management System
%   
%        \vspace{3.5cm}
%        \LARGE
%        Gustavo Adolfo Velasco-Hernandez
%        
%        \vfill
%        \large
%		        
%        
%        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
%        
%        \vspace{2cm}
%        
%        Advisor: Prof. Eduardo Caicedo Bravo
%		
%		\vspace{2cm}
%        
%        %\includegraphics[width=0.4\textwidth]{university}
%        Perception and Intelligent Systems Research Group \\
%        School of Electrical and Electronics Engineering\\
%        Universidad del Valle\\
%        Colombia\\
%        \today
%\vfill
\todo{Update version message and link}
Version: 1.1 \\
\vspace{2cm}

\end{center}

Check for an updated version at github: 
\href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}

\subsection*{Revision history}
\subsubsection*{Version 1.1 - 2019-01-24:}

	\begin{itemize}
	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
	\item Fixed V2I description in figure 1.6 (1.2.1)
	\item Reworded description of processing stages in section 2.1.1
	\item Described three transportation simulation models (2.2.1)
	\end{itemize}

\subsubsection*{Version 1.0 - 2018-09-21:}
	\begin{itemize}
	\item Initial version
	\end{itemize}

\end{titlepage}
